Our Title

### 2015-05-06 draft.tex
Merged in James K's additions to the "Limitations and Assumptions" section.

\section{Limitations and assumptions of this report (group 1)}

\subsection{?????? Julie working on this section ?????}

This policy recommendation is oriented primarily towards responding and preventing ISIL nuclear capabilities. The scope encompasses strategic communication within the intelligence community as well as among the U.S and potential countries and international entities and military capability. In the interest of time, this recommendation will not consider collaboration on information gathering or post-detonation. The following policy initiative will focus on developing an integrated intelligence strategy.

>>>>

\section{Limitations and Assumptions of this Report}

\subsection{?????? Needs content proofing ?????}

This report and policy recommendation covers a sensitive and poorly understood subject: ISIL and the possibility of their acquisition of nuclear materials, or in the worst case, weapons of mass destruction (WMD). The combination of unknowns in this situation with the limited abilities and experience of the authors results in several limitations:

\begin{itemize}
  \item The principle limitation is ISIL themselves and the broad lack of information and deep understanding of their goals and the methods they are willing to employ.
  \item The authors have no access to classified information and therefore are not privy to the most up-to-date information on current international strategies and capabilities of all parties involved in the following discussion and recommendations.
  \item As a whole, the authors have very limited experience in this field; this is not a complaint on the authors' part, but must be understood and accepted to understand the biases and limitations of this report.
  \item Per the definition of this assignment, the authors are limited in their analysis and discussion to the scenario of ISIL attempting to acquire WMD; post-acquisition will be touched on briefly but should be analyzed in depth in a future report and policy recommendation.
\end{itemize}

These limitations are important to understand before analysis and discussion can be had and policy recommendations can be made. To move forward, several assumptions are made:

\begin{itemize}
  \item The United States is interested in stopping ISIL from acquiring a nuclear weapon and willing to act decisively on this decision.
  \item ISIL does want to acquire WMD and will act decisively on this desire.
  \item All other assumptions are more specific and detailed and will be discussed in further depth throughout this report.
\end{itemize}

This policy recommendation is oriented primarily towards responding and preventing ISIL nuclear capabilities. The scope encompasses strategic communication within the intelligence community as well as among the U.S. and potential countries and international entities and military capability. In the interest of time, this recommendation will not consider collaboration on information gathering or post-detonation. The following policy initiative will focus on developing an integrated intelligence strategy.
